dispRity manual

### 2016-06-10 doc/dispRity-ecology-demo.Rmd
test-disparity problem when distributions are equal
Updated manuals

```{r}
##<!--, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>= -->
## The x and y axis represent the two first dimensions (i.e. principal
## components) of the ordination
x <- ord_matrix[, 1]
y <- ord_matrix[, 2]
## The colors will represent the treatments
cols <- sub("a", "red", treatments)
cols <- sub("b", "blue", cols)
## The symbols will represent the depth
pchs <- sub(1, 16, depth)
pchs <- as.numeric(sub(2, 17, pchs))

@@

![image](figure/minimal-PCAplot-1){width=".8\linewidth"}

@@

```{r}
## Graphical options
quartz(width = 10, height = 5) ; par(mfrow = (c(1,2)), bty = "n")

@@

![image](figure/minimal-rare_plots-1){width="1\linewidth"}

>>>>

```{r, fig.width=6, fig.height=6}
## The x and y axis represent the two first dimensions (i.e. principal
## components) of the ordination
x <- ord_matrix[, 1]
y <- ord_matrix[, 2]
## The colors will represent the treatments
cols <- sub("a", "red", treatments)
cols <- sub("b", "blue", cols)
## The symbols will represent the depth
pchs <- sub(1, 16, depth)
pchs <- as.numeric(sub(2, 17, pchs))

@@

@@

```{r, fig.width=6, fig.height=6}
## Graphical options
quartz(width = 10, height = 5) ; par(mfrow = (c(1,2)), bty = "n")

@@

### 2016-06-10 doc/dispRity-manual.Rmd
Updated manuals

```{r}
## Loading the package
library(dispRity)

@@

![image](figure/minimal-data-1){width=".8\linewidth"}

@@

```{r}
## Splitting the data
sliced_data <- time.series(BeckLee_mat99, BeckLee_tree, method = "continuous",
    model = "acctran", time = rev(seq(from=0, to=130, by=15)),
    FADLAD = BeckLee_ages)

@@

![image](figure/minimal-Quick_go-1){width=".5\linewidth"}

@@

```{r}
## Graphical options
quartz(width = 15, height = 5) ; par(mfrow = (c(1,3)), bty = "n")

@@

![image](figure/minimal-plot1-1){width="1\linewidth"}

@@

```{r}
## Graphical options
par(bty = "n")
## The rarefaction curves
plot(disp_crown_stemBS, elements = TRUE, rarefaction = "plot")

@@

![image](figure/minimal-plot2-1){width="0.5\linewidth"}

@@

![image](figure/minimal-plot3-1){width=".8\linewidth"}

@@

```{r}
## Graphical options
par(bty = "n")

@@

![image](figure/minimal-plot4-1){width=".5\linewidth"}

@@

```{r}
## Graphical options
par(bty = "n")
## A plot with many options!
plot(disp_time_slicesBS, quantile = c(seq(from=10, to=100, by=10)),
    cent.tend = sd, type = "continuous", elements = "log",
    col = c("black", rainbow(10)), ylab = c("Disparity", "log(Diversity)"),
    xlab = "Time (in in units from past to present)", time.series = FALSE,
    observed = TRUE, main = "Many options...")
```

![image](figure/minimal-plot5-1){width=".8\linewidth"}

@@

![image](figure/minimal-plot5_1-1){width=".5\linewidth"}

@@

## Measuring the overlap between distributions in the time bins (using the
## implemented Bhattacharyya Coefficient function - see ?bhatt.coeff) with a
## personalised series comparisons and some additional arguments to pass to the
## test function (bw = bw.nrd)
test.dispRity(disp_time_binsBS, test = bhatt.coeff, bw = bw.nrd,
    comparisons = list(c(1,2), c(1,3), c(2,1), c(3,1)))

>>>>

```{r, fig.width=6, fig.height=6}
## Loading the package
library(dispRity)

@@

@@

```{r, fig.width=6, fig.height=6}
## Splitting the data
sliced_data <- time.series(BeckLee_mat99, BeckLee_tree, method = "continuous",
    model = "acctran", time = rev(seq(from=0, to=130, by=15)),
    FADLAD = BeckLee_ages)

@@

@@

```{r, fig.width=6, fig.height=6}
## Graphical options
quartz(width = 15, height = 5) ; par(mfrow = (c(1,3)), bty = "n")

@@

@@

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## The rarefaction curves
plot(disp_crown_stemBS, elements = TRUE, rarefaction = "plot")

@@

@@

@@

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")

@@

@@

```{r, fig.width=6, fig.height=6}
## Graphical options
par(bty = "n")
## A plot with many options!
plot(disp_time_slicesBS, quantile = c(seq(from=10, to=100, by=10)),
    cent.tend = sd, type = "continuous", elements = "log",
    col = c("black", rainbow(10)), ylab = c("Disparity", "log(Diversity)"),
    xlab = "Time (in in units from past to present)", time.series = FALSE,
    observed = TRUE, main = "Many options...")
```

@@

@@

## Measuring the overlap between distributions in the time bins (using the
## implemented Bhattacharyya Coefficient function - see ?bhatt.coeff)
test.dispRity(disp_time_binsBS, test = bhatt.coeff)
